Implications of afforestation policies for global markets

### 2024-02-27 paper.Rmd
Update paper.Rmd

By joining these two models and passing outputs back and forth between the models, any limitations of either model should be minimized and more robust results, therefore, should be attained. Establishing a connection between the standard GTAP model and the GTM model required  a two-step process. First, we identified the set of common variables that are included in both models and their closures. That is, we selected which variables would be determined endogenously by one model and held as exogenous in the other model. In our case, we modeled the return on land using the GTAP model and fed those results into the GTM model as exogenous. Then, the amount of land available for crop and livestock production was endogenously determined by the GTM model and fed into the GTAP model as an exogenous input. In the second step, we established the connection between the models on the software level. This step required that the GTAP model, which is written in GEMPACK, be able to handle with the inputs from the GTM model, which is written in GAMS, and submit the outputs back to the GTM model. As GEMPACK and GAMS were developed long before software integration became important or even possible, we had to create a set of user functions in R that executed both models, collected their outputs, and created parameter files automatically.

Once R was able to operate both models automatically, we were then able to formulate the combined solution as a fairly simple math program that is solved in R:

>>>>

The rationale for joining these two models is that, by passing outputs back and forth between the models until an dual-state equilibrium is achieved, any limitations of either model should be minimized and more robust results should, therefore, be attained. Establishing a connection between the  GTAP model and the GTM model required a two-step process. First, we had to identify the set of variables that are common to both models and their closures. From those, we selected which variables would be determined endogenously by one model and held as exogenous in the other model. In our case, we decided to model the return on land using the GTAP model and feed those results into the GTM model as exogenous. The GTM model then endogenously determined the amount of land available for crop and livestock production, and we fed that back into the GTAP model as an exogenous input. In the second step, we established the connection between the models on the software level. This step required that the GTAP model, which is written in GEMPACK, be able to handle inputs from the GTM model, which is written in GAMS, and submit the outputs back to the GTM model. As GEMPACK and GAMS were developed long before software integration became important or even possible, we settled on the use of R [@R2021] to create the user functions that executed both models, collected their outputs, and automatically created parameter files.

Once R was able to control the interactions between both models, we were then able to formulate the combined solution as a fairly simple math program that is solved in R:
